### 2019-04-26 Old stuff/Results.Rmd
Rename Results.Rmd to Old stuff/Results.Rmd

We analyseed data from `r sum(data.sets$multi.centre.vs.single.centre$multi.centre$.imp == 0) ` trauma patients. The high and low centre samples contains `r sum(data.sets$high.volume.vs.low.volume$high.volume$.imp==0) ` and `r sum(data.sets$high.volume.vs.low.volume$low.volume$.imp==0)` trauma patients respectively (Table 1). The metropolitan sample and the non-metropolitan sample contains `r sum(data.sets$metropolitan.vs.non.metropolitan$metropolitan$.imp==0) ` and `r sum(data.sets$metropolitan.vs.non.metropolitan$non.metropolitan$.imp==0) ` respectively (Table 2). The multi centre sample constitutes the total number of trauma patients. We identified only one valid single centre. This single centre was identified as Karolinska Sjukhuset in Stockholm and contains `r  sum(data.sets$multi.centre.vs.single.centre$single.centre.11001$.imp==0) ` trauma patients (Table 3). The data presented in each table is multiple imputed. The number of imputations used is `r number.of.imputations  `, which is equal to the maximum percentage of missing data found across the data sets.

>>>>

We analyseed data from `r sum(data.sets$multi.centre.vs.single.centre$multi.centre$.imp == 0) ` trauma patients. The high and low centre samples contains `r sum(data.sets$high.volume.vs.low.volume$high.volume$.imp==0) ` and `r sum(data.sets$high.volume.vs.low.volume$low.volume$.imp==0)` trauma patients respectively (Table 1). The metropolitan sample and the non-metropolitan sample contains `r sum(data.sets$metropolitan.vs.non.metropolitan$metropolitan$.imp==0) ` and `r sum(data.sets$metropolitan.vs.non.metropolitan$non.metropolitan$.imp==0) ` respectively (Table 2). The multi centre sample constitutes the total number of trauma patients. We identified only one valid single centre. which contains `r  sum(data.sets$multi.centre.vs.single.centre$single.centre.11001$.imp==0) ` trauma patients (Table 3). The data presented in each table is multiple imputed. The number of imputations used is `r number.of.imputations  `, which is equal to the maximum percentage of missing data found across the data sets.
